Constrained Natural Language Parser for Semantic Web Based Policies

### 2009-08-14 paper/paper.tex
Re-wrote the introduction.

In this paper, we propose the Policy Parser, a system for translating
policies and rules in a natural language into an equivalent RDF
representation. The Policy Parser uses
templates to convert informal but structurally-constrained sentences into 
machine-readable policies, which are expressed in the
Accountability In RDF (AIR) policy language. A sentence is parsed
using a feature-based context-free grammar, which extracts semantic
information from the sentence to build a corresponding parse tree. The
information contained in the parse tree is then processed to build
an AIR policy. AIR policies are represented as Turtle statements and
can be used to express security and privacy constraints in a variety
of ontologies. We present a Firefox sidebar extension as the user interface for this
system, and we believe that it provides a natural interface for authoring
policies in RDF.

@@

Lawyers work with laws and policies all the time. They also determine given a scenario and a set of policies, whether a particular sequence of events in this scenario violates one or more of the given policies. Enforcing policies can be a challenging and error-prone process, as the number of policies gets larger or the scenario itself becomes more complex. In some cases, for example enforcing privacy policies governing access to data on the World Wide Web, manual enforcement of policies is particularly inefficient. Fortunately, some parts of the policy enforcement process are purely deductive reasoning, and therefore, can be automated by a computer.

The AIR reasoner\cite{air} takes input policies and scenarios expressed in RDF and determines whether or not the given scenario violates any of the given policies. One of the current barriers to wide spread use of AIR, or any other semantic web policy language is that it requires the user (person who specifies the policies; often a lawyer) of the system to write the AIR policies in RDF. Although RDF is a well-known within the Semantic Web community, it is likely that most lawyers will not be well versed in its use. Even for someone who is an expert in RDF, translating a natural language policy into RDF can be tedious and a time-consuming task. It thus becomes difficult to create and update policies that can be enforced automatically.

As a first step towards addressing these challenges, we have built the Policy Parser, which takes a policy, written in constrained natural language, and automatically translates it into its RDF representation.

>>>>

We propose the Policy Parser, a system for translating
policies and rules in a natural language into an equivalent RDF
representation. The Policy Parser uses templates to convert informal
but structurally-constrained sentences into machine-readable
policies, which are expressed in the Accountability In RDF (AIR)
policy language. A sentence is parsed using a feature-based
context-free grammar, which extracts semantic information from the
sentence to build a corresponding parse tree. The information
contained in the parse tree is then processed to build an AIR
policy. AIR policies are represented as Turtle statements and can be
used to express security and privacy constraints in a variety of
ontologies. We present a Firefox sidebar extension as the user
interface for this system. We believe that it provides a natural
interface for authoring policies in RDF.

@@

The growth in the sheer volume and variety of information on the web
shows no signs of slowing down, and electronic information systems are
attracting a wider range of users than ever. Administrators of these
systems face a challenging task: determining and enforcing policies
for controlling the access of information.

Unfortunately, many of the existing systems do not posess the
capacity to keep up with the rapid expansion of the data set and the
user base. The functionality for policy enforcement is often built
into a system during its initial development. As a result, access
control in most of these systems is rather limited and inflexible to changes.
As a need for new policies arises or usage scenarios grow
more complex, the administrator may need to modify parts of the system
that are responsible for maintaining and enforcing the policies. This
can be a costly and error-prone process.

Furthermore, the creator and the maintainer of the policy may be
different from the original developer of the system. Therefore, the
system must also provide a mechanism for transforming policies, 
which are often incepted as natural language sentences, into a precise
form that can be understood by the enforcement module.

We propose a potential solution to these challenges. Our prototype
system, called the Policy Parser, consists of two major parts:
(1) a graphical front-end, which translates an input natural language policy
into a set of RDF tuples, and (2) the Accountability In RDF (AIR)
reasoner, which automatically carries a series of logical
deductions to check whether a policy is enforced by a particular usage
scenario. The front-end uses templates to capture and extract
essential components of a policy and translate them into RDF tuples;
it can be easily extended with additional templates as the types of
policies diversify. Many forms of policy enforcement are
reducible to the logical reasoning that can be performed by the AIR
reasoner. Thus, even when policies undergo changes, the
underlying enforcement engine in our system need not be modified.

%Lawyers work with laws and policies all the time. They also determine given a scenario and a set of policies, whether a particular sequence of events in this scenario violates one or more of the given policies. Enforcing policies can be a challenging and error-prone process, as the number of policies gets larger or the scenario itself becomes more complex. In some cases, for example enforcing privacy policies governing access to data on the World Wide Web, manual enforcement of policies is particularly inefficient. Fortunately, some parts of the policy enforcement process are purely deductive reasoning, and therefore, can be automated by a computer.

%The AIR reasoner\cite{air} takes input policies and scenarios expressed in RDF and determines whether or not the given scenario violates any of the given policies. One of the current barriers to wide spread use of AIR, or any other semantic web policy language is that it requires the user (person who specifies the policies; often a lawyer) of the system to write the AIR policies in RDF. Although RDF is a well-known within the Semantic Web community, it is likely that most lawyers will not be well versed in its use. Even for someone who is an expert in RDF, translating a natural language policy into RDF can be tedious and a time-consuming task. It thus becomes difficult to create and update policies that can be enforced automatically.

%As a first step towards addressing these challenges, we have built the Policy Parser, which takes a policy, written in constrained natural language, and automatically translates it into its RDF representation.
